Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-12 doc/PRF2022/PRF_main.tex
minor checks

The Results section showed that 
variations in free energy and strain 
generally depend the distribution
of fluid stresses i.e. shear versus TG flow.   
To further illustrate how fluid stresses interact with the geometry of the JP
phases, we considered the initially circular vesicle bilayer
for various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). 
In all cases, the vesicle and TG flow reach a steady-state tank-treading motion,
but the geometry and motion varies nonmonotonically. 
For $\lambda$ ranging from $1$ nm to $4$ nm,
the steady-state vesicle shape goes from an octagon, to a dimpled square,
to a rounded diamond. \hl{Surprisingly, the direction of rotation switches,
so that for $\lambda = 1$ nm, the rotation is counterclockwise while
for $\lambda = 3$ nm, the rotation is clockwise, for example.  }
Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,
initial length $L_0$). 
As shown in Figure~\ref{fig:PramChange}(f), the relative
area $A/A_0$ achieves a steady-state that is greatest for $\lambda = 4$ nm
yet least for $\lambda = 2$ nm. 
(The relative length $L/L_0$, however, is
constant in $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e),
inset)).

>>>>

The Results section showed that 
variations in free energy and strain 
generally depend the distribution
of fluid stresses i.e. shear versus TG flow.   
To further illustrate how fluid stresses interact with the geometry of the JP
phases, we considered the initially circular vesicle bilayer
for various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). 
In all cases, the vesicle and TG flow reach a steady-state tank-treading motion,
but the geometry and motion varies nonmonotonically. 
For $\lambda$ ranging from $1$ nm to $4$ nm,
the steady-state vesicle shape goes from an octagon, to a dimpled square,
to a rounded diamond. Surprisingly, the direction of rotation switches,
so that for $\lambda = 2$ nm, the rotation is clockwise while
for $\lambda = 4$ nm, the rotation is counterclockwise, for example. 
Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,
initial length $L_0$). 
As shown in Figure~\ref{fig:PramChange}(f), the relative
area $A/A_0$ achieves a steady-state that is greatest for $\lambda = 4$ nm
yet least for $\lambda = 2$ nm. 
(The relative length $L/L_0$, however, is
constant in $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e),
inset)).
